Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-19 cav2017/cav2017.tex
review 1.1 Related Work

\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}

@@

In \cite{DBLP:journals/corr/AbateBCCDKK16}, Abate et al.  focus on
synthesising stabilizing controllers for continuous plants.  While
they also make use of a CEGIS-based technique, their approach is
restricted to synthesising controllers for hybrid closed-loop systems
that are stable and only consider transfer function models.  In contrast,
in the current paper we consider a state-space
representation of the physical system and synthesise controllers that
make the closed-loop system safe.  Moreover, 
a key aspect of our approach
is the fact that we integrate abstraction
refinement inside the CEGIS loop.

@@

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analyses
in~\cite{DBLP:conf/hybrid/WangGRJF16,DBLP:conf/hybrid/RouxJG15} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Programming (SDP).  While the former uses BIBO properties to determine
stability, the latter uses Lyapunov-based quadratic invariants.  In both
cases, the SDP solver uses floating-point arithmetic and soundness is
checked by bounding the error.  An alternative approach is taken
by~\cite{park2016scalable}, where the verification of existing code is
performed against a known model by extracting an LTI model of the code
through symbolic execution.  In order to account for rounding errors, an
upper bound is introduced in the verification phase.
The work in \cite{picasso2002construction,picasso2003stabilization} introduces
attractive invariant sets as a mechanism to bound the quantization error effect
on stabilization as an invariant set that always converges toward the cotrollable
set. In a similar fashion, \cite{liberzon2003hybrid} evaluates the dynamics of the
quantization error and binds their trajectory to a known region over a finite
period of time. This technique works for both linear and non-linear systems.
This paper uses an approach that projects the maximum effect of the noise over
an unbounded time and uses it as a `buffer' region for the safety specification.

@@

\begin{figure}[htb]
{\scriptsize
\centering
%\resizebox{.8\textwidth}{!}
{
 \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=.6cm, column sep=.9cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \coordinate (aux3);
   \& \coordinate (aux4);
   \&;\\
   \coordinate (aux5);
   \& \coordinate (aux6);
   \&;\\
   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=8cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc Verify},] (verif) {};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2.9cm]verif.center) {{\sc Uncertainty}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=-0.8cm]verif.center) {{\sc Precision}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=1.2cm]verif.center) {{\sc Sampling}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc Complete}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \& \\
   \node[minimum height=0cm] (gp) {\sf Closed-loop \\ System Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2.9cm]aux.center) {\sf BMC-based \\Verifier};
   \node (fp)  at ([xshift=-.8cm]aux.center) {\sf Fixed-point \\ Arithmetic\\Verifier};
   \node (sv)  at ([xshift=1.2cm]aux.center) {\sf Sampling\\Verifier};
   \node (cv)  at ([xshift=3.1cm]aux.center) {\sf Completeness\\Verifier};
   }   
    \\
  };

   \path
    ([yshift=2em]synth.east) edge node[xshift=-0.5em,align=center] {$P$} ([yshift=2em]verif1.west)
    ([yshift=-2em]verif1.west) edge node {C-ex} ([yshift=-2em]synth.east)
    ([xshift=-5em]fp.north) edge node[align=center]  {T/F} ([xshift=-5em]verif2.south)
    ([xshift=-5em]sv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif3.south)
    ([xshift=-5em]cv.north) edge node[align=center]  {T/F} ([xshift=-5em]verif4.south)
    ([xshift=5em]verif1.south) edge node[align=center] {$P$} ([xshift=5em]bmc.north)
    ([xshift=5em]verif2.south) edge node[align=center] {$P$} ([xshift=5em]fp.north)
    ([xshift=5em]verif3.south) edge node[align=center] {$P$} ([xshift=5em]sv.north)
    ([xshift=5em]verif4.south) edge node[align=center] {$P$} ([xshift=5em]cv.north)
    ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
    (verif) edge node {} (done)
    ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
    ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\$P$} ([xshift=-5em]synth.south)
    (aux1) edge (synth.north);
   \path[-]
   (verif2.north) edge node[align=center] {} ([xshift=-2.7cm]aux6)
   ([xshift=-2.7cm]aux6) edge node[align=center] {Increase Precision} (aux5)
   (verif3.north) edge node[align=center] {} ([xshift=4cm]aux4)
   ([xshift=4cm]aux4) edge node[align=center] {Increase Sampling Rate} (aux3)
   (verif4.north) edge node[align=center] {} ([xshift=10.5cm]aux2)
   ([xshift=10.5cm]aux2) edge node[align=center] {Increase $k$} (aux1);

 \end{tikzpicture}
}}
\caption{The CEGIS loop with precision and sampling rate incrementation}
\label{fig:CEGIS}
\end{figure}

>>>>

\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows, patterns}

@@

In \cite{DBLP:journals/corr/AbateBCCDKK16}, Abate et al.  focus on
synthesising stabilizing controllers for continuous plants
by exploiting advantage in bit-accurate verification of C programs 
to obtain a verifier for software-implemented digital control~\cite{Bessa16}.  
While they also make use of a CEGIS-based technique, their approach is
restricted to synthesising controllers for hybrid closed-loop systems
that are stable and only consider transfer function models.  In contrast,
in the current paper, we consider a state-space
representation of the physical system and synthesise controllers that
make the closed-loop system safe.  Moreover, 
a key aspect of our approach
is the fact that we integrate abstraction
refinement inside the CEGIS loop.

@@

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analyses
in~\cite{DBLP:conf/hybrid/RouxJG15,DBLP:conf/hybrid/WangGRJF16} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Programming (SDP).  While the former uses BIBO properties to determine
stability, the latter uses Lyapunov-based quadratic invariants.  In both
cases, the SDP solver uses floating-point arithmetic and soundness is
checked by bounding the error.  An alternative approach is taken
by~\cite{park2016scalable}, where the verification of existing code is
performed against a known model by extracting an LTI model of the code
through symbolic execution.  In order to account for rounding errors, an
upper bound is introduced in the verification phase.
The work in \cite{picasso2003stabilization,picasso2002construction} introduces
attractive invariant sets as a mechanism to bound the quantization error effect
on stabilization as an invariant set that always converges toward the cotrollable
set. In a similar fashion, \cite{liberzon2003hybrid} evaluates the dynamics of the
quantization error and binds their trajectory to a known region over a finite
period of time. This technique works for both linear and non-linear systems.
This paper uses an approach that projects the maximum effect of the noise over
an unbounded time and uses it as a `buffer' region for the safety specification.

@@

% \begin{figure*}[htb]
% \centering
% %\resizebox{1\textwidth}{!}
% {
%  \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
%   \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
% },
%           row sep=.6cm, column sep=2cm] {
%    \coordinate (aux1);
%    \& \coordinate (aux2);
%    \&;\\
%    \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
%    \&
%    complexnode/.pic={ 
%      \node[rectangle,draw,dotted,
% 	minimum width=7cm,
% 	minimum height=1cm,
%         pattern=north west lines, pattern color=gray!20,
% 	label={\sc Verify},] (verif) {};
%      \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc Uncertainty}};
%      \node[minimum width=2.5cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=2cm]verif.center) {{\sc Precision}};
%    } 
%    \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
%    %% \node[fill=yellow!20] (verif) {{\sc ~~~~~~Uncertainty~~~~~~}};
%    %% \&
%    %% \node[fill=yellow!20] (verif2) {{\sc ~~~~~~Precision~~~~~~~}};\\
%    \& \\
%    \node[minimum height=0.5cm] (gp) {\sf Closed-loop System Search};
%    \&
%    complexnode/.pic={ 
%      \coordinate (aux);
%    \node[minimum height=0.5cm] (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based Verifier};
%    \node[minimum height=0.5cm] (fp)  at ([xshift=2cm]aux.center) {\sf Fixed-point Arithmetic Verifier};
%    }   
%     \\
%   };

%    \path
%     ([yshift=2em]synth.east) edge node[xshift=-0.5em] {Candidate solution} ([yshift=2em]verif1.west)
%     ([yshift=-2em]verif1.west) edge node {Counterexample} ([yshift=-2em]synth.east)
%     ([xshift=5em]verif1.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]bmc.north)
%     ([xshift=5em]verif2.south) edge node[align=center] {Candidate\\ $P$} ([xshift=5em]fp.north)
%     ([xshift=-5em]bmc.north) edge node[align=center]  {UNSAT/\\model} ([xshift=-5em]verif1.south)
%     ([xshift=-5em]fp.north) edge node[align=center]  {True/\\False} ([xshift=-5em]verif2.south)
%     (verif2) edge node {} (done)
%     ([xshift=5em]synth.south) edge node[align=center] {Inputs} ([xshift=5em]gp.north)
%     ([xshift=-5em]gp.north) edge node[align=center] {UNSAT/\\candidate} ([xshift=-5em]synth.south)
%     (aux1) edge (synth.north);
%    \path[-]
%    (verif2.north) edge node[align=center] {} ([xshift=6.7cm]aux2)
%    ([xshift=6.7cm]aux2) edge node[align=center] {Increase Precision} (aux1);

%  \end{tikzpicture}
% }
% \caption{The CEGIS loop with precision and sampling rate incrementation}
% \label{fig:CEGIS}}
% \end{figure*}
